### 2015-05-08 fundamentals/fcsreqs.tex
reviewer 2:page 6: typing errors: ...facilitate... ...particular agent

\subsubsection{Discrete Facilities and Materials}
Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\DIFdelbegin 
\DIFdel{\mbox{%DIFAUXCMD
\gls{DESAE} \cite{andrianova_desae_2008}
}%DIFAUXCMD
, }\DIFdelend FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.

>>>>

\subsubsection{Discrete Facilities and Materials}

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\gls{DESAE}
\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.
